---
title: "p8105_hw1_yl5508"
author: "Felix LIU"
output:
  html_document:
   toc: TRUE
   toc_float: TRUE
   code_folding: hide
---

It's a proj for HW1 about BUILDING BLOCKS.

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```

## Q1

### Q1.1 DATA OVERVIEW

Before we start, we need to download the dataset by `install.packages("moderndive")`.  

Use `library(moderndive)` and `data("early_january_weather")` to load the data.  

```{r, echo = FALSE}
library(moderndive)
data("early_january_weather")
```

Then, use `view(early_january_weather)` and `?early_january_weather` to check data info.  

**Data Info**:  
**(a) overview:** Hourly meterological data for LGA, JFK and EWR for the month of January 2013. This is a subset of the weather data frame from nycflights13.  
**(b) variables:** `origin` is weather station, `year, month, day, hour` is time of recording. Then, there are some weather index variables, like `temp(temperature in F)`, `dewp(dewpoint)`, `humid(ralative humidity)`, `wind_dir(Wind direction in degrees)`, `wind_speed(in mph)`, `wind_gust(gust speed in mph)`, `precip(precipitation in inches)`, `pressure(sea level pressure in millibars)`, `visib(visibility in miles)`, `time_hour(Date and hour of the recording)`.
**(c) the size of dataset** is `r nrow(early_january_weather)` X `r ncol(early_january_weather)`.  
**(d) the average temperature** is `r round(mean(early_january_weather$temp), 1)`.

### Q1.2 SCATTERPLOT

We can get a scatter plot (temp vs time_hour) from the dataset.  
Specifically, `ggplot()` and `geom_point()` is used to depict basic scatter plot (color in humid), `geom_smooth()` is to generate a fitted curve of the scatter plot.  
Then, the plot is saved as "scatterplot_yl5508.png".

```{r yx_scatter, message = FALSE}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = "humid")) + 
  geom_point() + 
  geom_smooth(span = 0.1, color = "lightgray") + 
  scale_x_datetime(date_breaks = "3 days") + 
  ggtitle("scatterplot of temp (y) vs time_hour (x)") + 
  theme(plot.title = element_text(hjust = 0.5), legend.position = "NONE")
ggsave("scatterplot_yl5508.png")
```





